\documentclass[
  man,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

\usepackage{amsmath}
\usepackage{amssymb}




\RequirePackage{longtable}
\RequirePackage{threeparttablex}

\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-.5em}%
	{\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-\z@\relax}%
	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother




\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

\usepackage{tcolorbox}
\tcbuselibrary{listings,theorems, breakable, skins}
\usepackage{fontawesome5}

\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}

%\newlength\Oldarrayrulewidth
%\newlength\Oldtabcolsep


\usepackage{hyperref}




\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}





\usepackage{newtx}

\defaultfontfeatures{Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}





\title{Integrative Taxonomy of North Atlantic \emph{Acanthocope} with
description of a new species}


\shorttitle{ACTCP}


\usepackage{etoolbox}









\authorsnames[{1},{2}]{Zhehao Hu,Jenny Neuhaus}







\authorsaffiliations{
{Department of Biology, University of Hamburg},{German Centre for Marine
Biodiversity Research, Senckenberg am Meer}}




\leftheader{Hu and Neuhaus}




\keywords{Integrative taxonomy, Isopoda, Deep-sea, Biogeography}

\authornote{\par{\addORCIDlink{Jenny Neuhaus}{0009-0000-7570-4094}} 

\par{       }
\par{Correspondence concerning this article should be addressed
to Zhehao Hu, Department of Biology, University of
Hamburg, Martin-Luther-King Platz
3, Hamburg D-20146, Email: hu\_zhehao@hotmail.com}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother
\RequirePackage{longtable}
\DeclareDelayedFloatFlavor{longtable}{table}

\urlstyle{same}



\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

% From https://tex.stackexchange.com/a/645996/211326
%%% apa7 doesn't want to add appendix section titles in the toc
%%% let's make it do it
\makeatletter
\xpatchcmd{\appendix}
  {\par}
  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
  {}{}
\makeatother

%% Disable longtable counter
%% https://tex.stackexchange.com/a/248395/211326

\usepackage{etoolbox}

\makeatletter
\patchcmd{\LT@caption}
  {\bgroup}
  {\bgroup\global\LTpatch@captiontrue}
  {}{}
\patchcmd{\longtable}
  {\par}
  {\par\global\LTpatch@captionfalse}
  {}{}
\apptocmd{\endlongtable}
  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
  {}{}
\newif\ifLTpatch@caption
\makeatother

\begin{document}

\maketitle


\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setlength\LTleft{0pt}


\subsection{About the manuscript}\label{about-the-manuscript}

Latest edition is online at
\href{https://zzzhehao.github.io/ACTCP/\#ACTCPFELIS}{https://zzzhehao.github.io/ACTCP/}

Password required: \texttt{ACTCPFELIS}

\textbf{Download}

\begin{itemize}
\tightlist
\item
  \textbf{MS Word} (APA 7 style manuscript), \textbf{PDF} (APA 7 style
  manuscript) and \textbf{MECA} bundle (Computation source code
  included) are available under ``Other Formats'' in the header banner
\end{itemize}

\textbf{Commenting}

\begin{itemize}
\tightlist
\item
  Register \href{https://hypothes.is/groups/6KpDgDmQ/actcp}{here
  (Hypothes.is)}
\item
  Use annotation to add comments, make sure to change group to ACTCP
  (private).
\item
  Or send comments, suggestion, edited MS Word file to
  \href{mailto:hu_zhehao@hotmail.com}{\nolinkurl{hu\_zhehao@hotmail.com}}
\end{itemize}

\subsection{Whiteboard}\label{whiteboard}

\subsubsection{03-07 \textbar{} 18S and TCS
Abstract}\label{s-and-tcs-abstract}

\begin{itemize}
\tightlist
\item
  A quick preview to the 18S phylogeny:
  \href{./notebooks/42\%20Result\%20-\%20Genetics.qmd}{genetic result}
\item
  Abstract for TCS Meeting Paris:
  \href{./notebooks/11\%20TCS-Abstract.qmd}{TCS Abstract}
\item
  All drawing scans are \href{./notebooks/51\%20Drawing.qmd}{here}
\end{itemize}

\subsubsection{02-28 \textbar{} Loan request ZMH
(Pending)}\label{loan-request-zmh-pending}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Type materials}
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \emph{A. puertoricana}: ZMH K--46195 (Holotype), ZMH K--46196, ZMH
  K--46198 (Puerto Rico Trench)
\item
  \emph{A. eleganta}: ZMH K--40716 (Holotype), ZMH K--40717, ZMH
  K--40718. (Weddell Sea)
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{ZMH K--46200}: \emph{A. eleganta}
\end{enumerate}

\emph{A. eleganta} morphologically identified by Malyutina et al.
(\citeproc{ref-malyutina2018}{2018}), found at the same station as
\emph{A. puertoricana} (Puerto Rico Trench). A big support that \emph{A.
eleganta} and \emph{A. puertoricana} are the same species if we can pull
genetics and proteomics from them.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \textbf{ZMH K--46199}: \emph{A. annulatus}
\end{enumerate}

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, leftrule=.75mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, breakable, colbacktitle=quarto-callout-note-color!10!white, bottomrule=.15mm, toprule=.15mm, bottomtitle=1mm, opacitybacktitle=0.6, coltitle=black, arc=.35mm, left=2mm, toptitle=1mm, opacityback=0, titlerule=0mm, rightrule=.15mm, colback=white]

Malyutina et al. (\citeproc{ref-malyutina2018}{2018}):

Acanthocope annulatus Menzies, 1962 (Fig. 16)

Acanthocope annulatus (Menzies, 1962: 155, Fig. 44 B, C; Malyutina and
Brandt, 2004: 11, Figs. 6--10. Material examined: 1 male (5.9 mm TL),
ZMH K--46199, Puerto Rico Trench abyssal area, RV Sonne, Vema-TRANSIT
cruise, 25 January 2015, C-EBS, station 14-1, 19°1.63′N 67°9.73′W,
4552‒4552 m depth, supranet, bottom temperature: 2.25 °C, bottom O2:
261.13 μM, bottom current: 5.25 cm/s.

Remarks: The only specimen of the species, found at the same station as
A. puertoricana sp. nov., was identified as it has all described
characters of the Acanthocope annulatus Menzies, 1962. This new record
is located at more than 10000 km far away from the type locality in the
southeastern Atlantic (SW of Cape Town). Future sampling in the Atlantic
and genetic investigations might shed some light on the true
distribution of this species.

\end{tcolorbox}

\subsection{Abstract}\label{abstract}

Science still struggles with reliable taxonomy that forms the foundation
for many subsequent studies on marine ecosystems. A case study with
integrative approach reports first phylogenetic understanding of the
genus \emph{Acanthocope} (Isopoda: Munnopsidae) as well as its
biogeography in the North Atlantic, in addition with the description of
a new species.

(\ldots{} more with results: Hybridization of Morphogroup 2? Confirm of
monophyly? etc.)

(\ldots{} what impact does this have? ``Contributing to current
understanding of evolution pattern of Munnopsidae''??)

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-malyutina2018}
Malyutina, M. V., Frutos, I., \& Brandt, A. (2018). Diversity and
distribution of the deep-sea {Atlantic Acanthocope} ({Crustacea},
{Isopoda}, {Munnopsidae}), with description of two new species.
\emph{Deep Sea Research Part II: Topical Studies in Oceanography},
\emph{148}, 130--150. \url{https://doi.org/10.1016/j.dsr2.2017.11.003}

\end{CSLReferences}






\end{document}
